### 2019-04-22 initial/notes.tex
more update notes

The effective probability of threading the opened gap between the
stable/unstable manifolds is then just $P \propto D\sin \psi \sim
\frac{2\pi}{T\p*{\eta \sin I}}$. Plugging in some observational values $T \sim
50, \eta = 0.1, I = 20^\circ$ gives $P \propto 0.13$. In reality, I find it
asymptotes to $\sim 0.08$, so the constant of proportionality is of order unity.
Not bad given the really crappy $\psi \sim
\frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.

@@

>>>>

The effective probability of threading the opened gap between the
stable/unstable manifolds is then just $P \propto D\sin \psi \sim
\frac{2\pi}{T\p*{\eta \sin I}}$. According to later analysis, this should really
be $\frac{2\pi}{T}$. Plugging in some observational values $T \sim 50$ for $\eta
= 0.1$gives $P \propto 0.13$. In reality, I find it asymptotes to $\sim 0.08$,
so the constant of proportionality is of order unity. Not bad given the really
crappy $\psi \sim \frac{\ev*{\dot{\theta}}}{\dot{\phi}}$ argument.

@@

We compute the maximum $\abs*{f(q^0)}$, which occurs at $\phi = \pi$, and we
find the expected $f \approx \sqrt{4\eta \sin I}$.
